Møil: A web-based administration tool for database-backed mail servers

### 2014-07-23 doc/paper/paper.tex
Use Guard for auto-building (despite the numerous dependencies).
Sketch for paper contents [skip ci].

	\title{Møil: A web-based administration tool for database-backed mail servers with postfix and dovecot}
	%\subtitle{}
	\author{
		Henning Müller $<$\href{mailto:henning@orgizm.net}{henning@orgizm.net}$>$
	}
	\date{}

@@

	\section*{Introduction and problem}
		% Usage examples:
		%	\cite{rest}
		%	\s after a paragraph for a little space
		%	\begin{description}
		%		\item[\rm Foo]\ \\
		%			Bar
		%	\end{description}

	\section*{Analysis of existing software}

	\subsection*{Criteria}

	\subsection*{The contestants}

	\section*{A new solution: Møil}

>>>>

	\title{Møil: A web-based administration tool for database-backed mail servers}
	\author{Henning Müller $<$\href{mailto:henning@orgizm.net}{henning@orgizm.net}$>$}
	\date{}

@@

	% Usage examples:
	%	\cite{rest}
	%	\s after a paragraph for a little space
	%	\begin{description}
	%		\item[\rm Foo]\ \\
	%			Bar
	%	\end{description}

	\section*{Introduction}
		For mail system setups (meaning one or more servers running Mail
		Submission, Delivery and Transfer Agent software and providing a
		Message Store for users \cite{mail-architecture}), storing data about
		which domains and E-Mail addresses the system is responsible for in
		databases is beneficial for several reasons.

		% Reasons for database-backing
		%	Structural clarity for administrators
		%	Horizontal scalability
		%	API (e.g. for accounting)
		% Query possibilities (LDAP, SQL)

	\section*{Evaluation of existing software}
		% Overview and inspiration

		\subsection*{Criteria}
			% Data model
			%	Structure (postfix.admin compatible?)
			%	Maintainability of schema
			%	Security (e.g. password hashing)
			% Responsiveness
			%	Terminal
			%	Desktop web browsers
			%	Mobile devices
			% Usability
			% Scalability (for user exposed functionality)
			% Features
			%	Basic domain, mailbox and alias management
			%	Password change for end users
			%	Privilege model
			%	Others
			%		Audit trail
			%		Vacation
			%		Spam frontend
			%		Sieve
			%		Webmail integration
			% Programming language
			% Containability (e.g. independence of Message Store file system)
			% Database independence

		\subsection*{The contestants}
			% PHP
			%	ratuus http://www.ratuus.org/
			%	ViMbAdmin http://www.vimbadmin.net/
			%	postfix.admin http://postfixadmin.sourceforge.net/
			% Perl
			%	VBox.Adm http://www.vboxadm.net/
			% Python
			%	modoboa http://modoboa.org

	\section*{A new solution: Møil}
		% Rails
		% Causes for a new solution
		%	Data model, migrations
		%	CLI
		%	Password hash generation for compatibility to older solution
		%	Other features

		\subsection*{Features}

		\subsection*{Architecture}
			% Modules

		\subsection*{Data model}
			% Data model
			%	Structure / ERD
			%	Migrations
			%	sha512-crypt

		\subsection*{Setup}
			% Relevant configs for postfix and dovecot
			% Setup of rails app
			% Links to README on GitHub
